Rapid cycleway prioritisation tool

### 2020-06-05 code/index.Rmd
Update index

The [rapid cycleway prioritisation tool](https://www.cyipt.bike/rapid/) helps identify promising locations for road space reallocation in England to create new cycleways.
Used with local knowledge, it provides a strong evidence base to support planning of rapid measures to support safe travel as part of the COVID-19 response.
The rational for the tool is that, in the context of COVID-19, big decisions need to be made quickly.
The tool aims to support fast yet informed decision making a 'first pass' to help focus planning attention on road sections that are most likely to be suitable for new schemes.

>>>>

The [rapid cycleway prioritisation tool](https://www.cyipt.bike/rapid/) helps identify promising locations for road space reallocation in England.
The tool provides an evidence base to support investment in cycling infrastructure, in response to new pressures placed on transport and public health systems by the COVID-19 crisis, at local and regional levels.
The rational for the tool is that, in the context of COVID-19, big decisions around where to prioritise investment on the road network need to be made quickly.
The tool provides a 'first pass' assessment of the existing road network to help focus planning attention on options that are likely to have sufficient space for new infrastructure in places where there is high latent demand.
